Misspecification Demonstration

### 2022-07-30 misspecification_study/misspec_demo.Rmd
figuring out OSA residual problem

# sim_input[[1]] has no data modification and em1
set.seed(14159265) #use same seed for all operating models
sim_input[[1]] = lapply(1:nsim, function(x) {
  input_i = em_input1
  sim = om$simulate(complete=TRUE)
  input_i$data = sim
  return(input_i)
})

# sim_input[[2]] uses the correct data and em2
sim_input[[2]] = lapply(1:nsim, function(x) {
  input_i = em_input2
  obs_names = c("agg_indices","agg_catch","catch_paa","index_paa", "Ecov_obs", "obsvec")
  input_i$data[obs_names] = sim_input[[1]][[x]]$data[obs_names]
  return(input_i)
})

# sim_input[[3]] uses the correct data and em3
sim_input[[3]] = lapply(1:nsim, function(x) {
  input_i = em_input3
  obs_names = c("agg_indices","agg_catch","catch_paa","index_paa", "Ecov_obs", "obsvec")
  input_i$data[obs_names] = sim_input[[1]][[x]]$data[obs_names]
  return(input_i)
})

# sim_input[[4]] uses the correct data and em4
sim_input[[4]] = lapply(1:nsim, function(x) {
  input_i = em_input4
  obs_names = c("agg_indices","agg_catch","catch_paa","index_paa", "Ecov_obs", "obsvec")
  input_i$data[obs_names] = sim_input[[1]][[x]]$data[obs_names]
  return(input_i)
})

@@

# sim_input[[6]] has under-reported catch and em2
sim_input[[6]] = lapply(1:nsim, function(x) {
  input_i = em_input2
  obs_names = c("agg_indices","agg_catch","catch_paa","index_paa", "Ecov_obs", "obsvec")
  input_i$data[obs_names] = sim_input[[5]][[x]]$data[obs_names]
  return(input_i)
})

# sim_input[[7]] has under-reported catch and em3
sim_input[[7]] = lapply(1:nsim, function(x) {
  input_i = em_input3
  obs_names = c("agg_indices","agg_catch","catch_paa","index_paa", "Ecov_obs", "obsvec")
  input_i$data[obs_names] = sim_input[[5]][[x]]$data[obs_names]
  return(input_i)
})

# sim_input[[8]] has under-reported catch and em4
sim_input[[8]] = lapply(1:nsim, function(x) {
  input_i = em_input4
  obs_names = c("agg_indices","agg_catch","catch_paa","index_paa", "Ecov_obs", "obsvec")
  input_i$data[obs_names] = sim_input[[5]][[x]]$data[obs_names]
  return(input_i)
})
```

@@

```{r plotemfit8}
# ran into errors plotting the one-step-ahead residuals for each model
# ran the loop one model at a time to get output
#
# em_fits 1 and 5 gave error message
# Error in mod$osa[c(dat$keep_Cpaa[i, yind, ] + 1), ] : 
#   incorrect number of dimensions
#
# the other six em_fits gave error message
# Infinite osa residuals for aggregate catch in fleet  1 , so using +/-10 for range of y axis 
# Error in if (h > 0) max(1, ceiling(diff(range(x))/h)) else 1L : 
#   missing value where TRUE/FALSE needed
# In addition: Warning messages:
# 1: In min(x) : no non-missing arguments to min; returning Inf
# 2: In max(x) : no non-missing arguments to max; returning -Inf

# can either pull this code out and run in console, or else uncomment and knit then comment and knit again
# out.dir <- file.path(here(), "misspecification_study", "output")
# if (!dir.exists(out.dir)){
#   dir.create(out.dir)
# }
# mydir <- c(paste0("CC_em", 1:4), paste0("UR_em", 1:4))
# for (i in 1:8){
#   em.dir <- file.path(here(), "misspecification_study", "output", mydir[i])
#   if(!dir.exists(em.dir)){
#     dir.create(em.dir)
#   }
#   plot_wham_output(mod=em_fits[[i]][[1]], dir.main=em.dir)
# }
```

>>>>

obs_names = c("agg_indices","agg_catch","catch_paa","index_paa", "Ecov_obs", "obsvec")

# sim_input[[1]] has no data modification and em1
set.seed(14159265) #use same seed for all operating models
sim_input[[1]] = lapply(1:nsim, function(x) {
  input_i = em_input1
  sim = om$simulate(complete=TRUE)
  input_i$data[obs_names] = sim[obs_names]
  return(input_i)
})

# sim_input[[2]] uses the correct data and em2
sim_input[[2]] = lapply(1:nsim, function(x) {
  input_i = em_input2
  input_i$data[obs_names] = sim_input[[1]][[x]]$data[obs_names]
  return(input_i)
})

# sim_input[[3]] uses the correct data and em3
sim_input[[3]] = lapply(1:nsim, function(x) {
  input_i = em_input3
  input_i$data[obs_names] = sim_input[[1]][[x]]$data[obs_names]
  return(input_i)
})

# sim_input[[4]] uses the correct data and em4
sim_input[[4]] = lapply(1:nsim, function(x) {
  input_i = em_input4
  input_i$data[obs_names] = sim_input[[1]][[x]]$data[obs_names]
  return(input_i)
})

@@

# sim_input[[6]] has under-reported catch and em2
sim_input[[6]] = lapply(1:nsim, function(x) {
  input_i = em_input2
  input_i$data[obs_names] = sim_input[[5]][[x]]$data[obs_names]
  return(input_i)
})

# sim_input[[7]] has under-reported catch and em3
sim_input[[7]] = lapply(1:nsim, function(x) {
  input_i = em_input3
  input_i$data[obs_names] = sim_input[[5]][[x]]$data[obs_names]
  return(input_i)
})

# sim_input[[8]] has under-reported catch and em4
sim_input[[8]] = lapply(1:nsim, function(x) {
  input_i = em_input4
  input_i$data[obs_names] = sim_input[[5]][[x]]$data[obs_names]
  return(input_i)
})
```

@@

```{r plotemfit8, eval = FALSE}
# ran into errors plotting the one-step-ahead residuals for each model
# ran the loop one model at a time to get output
#
# em_fits 1 and 5 gave error message
# Error in mod$osa[c(dat$keep_Cpaa[i, yind, ] + 1), ] : 
#   incorrect number of dimensions
#
# the other six em_fits gave error message
# Infinite osa residuals for aggregate catch in fleet  1 , so using +/-10 for range of y axis 
# Error in if (h > 0) max(1, ceiling(diff(range(x))/h)) else 1L : 
#   missing value where TRUE/FALSE needed
# In addition: Warning messages:
# 1: In min(x) : no non-missing arguments to min; returning Inf
# 2: In max(x) : no non-missing arguments to max; returning -Inf

# can either pull this code out and run in console, or else uncomment and knit then comment and knit again
out.dir <- file.path(here(), "misspecification_study", "output")
if (!dir.exists(out.dir)){
  dir.create(out.dir)
}
mydir <- c(paste0("CC_em", 1:4), paste0("UR_em", 1:4))
for (i in 1:8){
  em.dir <- file.path(here(), "misspecification_study", "output", mydir[i])
  if(!dir.exists(em.dir)){
    dir.create(em.dir)
  }
  plot_wham_output(mod=em_fits[[i]][[1]], dir.main=em.dir)
}
```
